---
title: "PracticalMachineLearning Assignment Writeup"
author: "Michael Kothakota"
date: "September 19, 2014"
output: html_document
---

We are examining data from fitness data collectors.  The goal is to determine whether someone did an exercise correctly or not.  

We will first load all of the libraries needed:

```{r}
library(caret)
library(ggplot2)
library(lattice)
library(kernlab)
library(rpart)
```

We'll then set the seed at 2009, read in the data, and split the Training data set into a training and test set.

```{r}
set.seed(2009)
setwd("~/Desktop")
data <- read.csv("pml-training.csv")
testdata <- read.csv("pml-testing.csv")
```

We will need to clean the data.  There are many columns that need to be removed.  

```{r}
newset <- data
newset[ newset == '' | newset == 'NA'] <- NA
exc <- which(colSums(is.na(newset))!=0)
newset <- newset[, -exc]
newset <- newset[,-(1:7)]
```

Once we remove those columns, we'll need to split the training set


```{r}
inTrain <- createDataPartition(y=newset$classe, p=0.6, list=FALSE)

train <- newset[inTrain,]
test <- newset[-inTrain,]
```



Build a Random Forest model

```{r}
RFMod <- train(classe ~., data=train, method="rf", tunelength=1, ntree=25)
RFMod
```

Examine the confusion matrix to determine how the "train" set performs versus the "test" set.

```{r}
confusionMatrix(predict(RFMod, train), train$classe)
```

We then want to look at the test data.  First we need to load the test data in.

Then we apply the prediction model from the training data and apply it:

```{r}
assign <- predict(RFMod, testdata)
assign
```

This data will be uploaded in text files for a grade.

